### 2016-08-26 RA-L/experiment.tex
Corrected the length of the table

Our experiments are on centimeter-scale hardware systems called \emph{kilobots}.  These allows us to emulate a variety of dynamics, while enabling a high degree of control over robot function, the environment, and data collection. The kilobot, from \citet{Rubenstein2012,rubenstein2014programmable} is a low-cost robot designed for testing collective algorithms with large numbers of robots. It is available as an open source platform or commercially from~\citet{K-Team2015}.  Each robot is approximately 3 cm in diameter, 3 cm tall, and uses two vibration motors to move on a flat surface at speeds up to 1 cm/s.  Each robot has one ambient light sensor that is used to implement \emph{phototaxis},  moving towards a light source. 
In these experiments as shown in Fig.~\ref{fig:setup}, we used $n$=100 kilobots, a 1.5 m$\times$1.2 m whiteboard as the workspace, and eight 30W LED floodlights arranged 1.5 m above the plane of the table at the $\{N,NE,E,SE,S,SW,W,NW\}$ vertices of a 6 m square centered on the workspace. The lights were controlled using an Arduino Uno board connected to an 8-relay shield.  Above  the table, an overhead machine vision system tracks the position of the swarm.

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{SetUp.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:setup}
Hardware platform:  table with 1.5$\times$1.2 m workspace, surrounded by eight remotely triggered 30W LED floodlights, with an overhead machine vision system.
}
\vspace{-1em}
\end{figure}
\subsection{Hardware Experiment: Position Control of Two Robots}
The walls of the hardware platform have almost infinite friction, due to a laser-cut, zigzag border and the three-legged design of the kilobots. When a kilobot is steered into the zigzag border, they pin themselves to the wall unless the global input directs them away from the wall.  This wall friction is sufficient to enable independent control of two kilobots, as shown in Fig.~\ref{fig:storyReal}.

>>>>

Our experiments are on centimeter-scale hardware systems called \emph{kilobots}.  These allows us to emulate a variety of dynamics, while enabling a high degree of control over robot function, the environment, and data collection. The kilobot, from \citet{Rubenstein2012,rubenstein2014programmable} is a low-cost robot designed for testing collective algorithms with large numbers of robots. It is available as an open source platform or commercially from~\citet{K-Team2015}.  Each robot is approximately 3 cm in diameter, 3 cm tall, and uses two vibration motors to move on a flat surface at speeds up to 1 cm/s.  Each robot has one ambient light sensor that is used to implement \emph{phototaxis},  moving towards a light source. 
In these experiments as shown in Fig.~\ref{fig:setup}, we used $n$=100 kilobots, a 1 m$\times$1 m whiteboard as the workspace, four 30W and four 50W LED floodlights arranged 1.5 m above the plane of the table at the $\{N,NE,E,SE,S,SW,W,NW\}$ vertices of a 6 m square centered on the workspace. The lights were controlled using an Arduino Uno board connected to an 8-relay shield.  Above  the table, an overhead machine vision system tracks the position of the swarm.

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{SetUp.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:setup}
Hardware platform:  table with 1$\times$1 m workspace, surrounded by eight remotely triggered LED floodlights, with an overhead machine vision system.
}
\vspace{-1em}
\end{figure}
\subsection{Hardware Experiment: Position Control of Two Robots}
The walls of the hardware platform have almost infinite friction, due to a laser-cut, zigzag border and the three-legged design of the kilobots. When a kilobot is steered into the zigzag border, they pin themselves to the wall unless the global input directs them away from the wall.  This wall friction is sufficient to enable independent control of two kilobots, as shown in Fig.~\ref{fig:storyReal}.
